Towards Practical First-Order Model Counting: Technical Appendix

### 2025-01-11 doc/old_paper/plot.tex
First draft of the SAT version

% Created by tikzDevice version 0.12.6 on 2024-08-07 14:16:35
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,106.36) --
	( 45.67,106.36) --
	( 51.24,106.36) --
	( 56.80,106.36) --
	( 62.37,106.36) --
	( 67.94,106.37) --
	( 73.50,106.38) --
	( 79.07,106.42) --
	( 84.64,106.58) --
	( 90.20,107.23) --
	( 95.77,109.99) --
	(101.34,117.90);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.10,123.48) --
	( 45.67,112.22) --
	( 51.24,112.22) --
	( 56.80,112.42) --
	( 62.37,119.02) --
	( 67.94,162.96);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 40.10,106.36) circle (  1.96);

\path[fill=fillColor] ( 45.67,106.36) circle (  1.96);

\path[fill=fillColor] ( 51.24,106.36) circle (  1.96);

\path[fill=fillColor] ( 56.80,106.36) circle (  1.96);

\path[fill=fillColor] ( 62.37,106.36) circle (  1.96);

\path[fill=fillColor] ( 67.94,106.37) circle (  1.96);

\path[fill=fillColor] ( 73.50,106.38) circle (  1.96);

\path[fill=fillColor] ( 79.07,106.42) circle (  1.96);

\path[fill=fillColor] ( 84.64,106.58) circle (  1.96);

\path[fill=fillColor] ( 90.20,107.23) circle (  1.96);

\path[fill=fillColor] ( 95.77,109.99) circle (  1.96);

\path[fill=fillColor] (101.34,117.90) circle (  1.96);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 38.14,121.52) --
	( 42.06,121.52) --
	( 42.06,125.44) --
	( 38.14,125.44) --
	cycle;

\path[fill=fillColor] ( 43.71,110.26) --
	( 47.63,110.26) --
	( 47.63,114.18) --
	( 43.71,114.18) --
	cycle;

\path[fill=fillColor] ( 49.27,110.26) --
	( 53.20,110.26) --
	( 53.20,114.18) --
	( 49.27,114.18) --
	cycle;

\path[fill=fillColor] ( 54.84,110.46) --
	( 58.76,110.46) --
	( 58.76,114.38) --
	( 54.84,114.38) --
	cycle;

\path[fill=fillColor] ( 60.41,117.06) --
	( 64.33,117.06) --
	( 64.33,120.99) --
	( 60.41,120.99) --
	cycle;

\path[fill=fillColor] ( 65.97,161.00) --
	( 69.90,161.00) --
	( 69.90,164.92) --
	( 65.97,164.92) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.68, 87.62) --
	(203.25, 87.61) --
	(208.82, 87.61) --
	(214.38, 87.61) --
	(219.95, 87.61) --
	(225.52, 87.61) --
	(231.08, 87.62) --
	(236.65, 87.69) --
	(242.22, 88.58) --
	(247.78, 97.29) --
	(253.35,123.32) --
	(258.92,157.55) --
	(264.48,192.33);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 87.37) --
	(203.25, 87.36) --
	(208.82, 87.36) --
	(214.38, 87.36) --
	(219.95, 87.36) --
	(225.52, 87.36) --
	(231.08, 87.37) --
	(236.65, 87.44) --
	(242.22, 88.34) --
	(247.78, 97.16) --
	(253.35,123.35) --
	(258.92,157.54) --
	(264.48,192.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (197.68,113.24) --
	(203.25,111.85) --
	(208.82,111.59) --
	(214.38,111.66) --
	(219.95,112.12) --
	(225.52,112.27) --
	(231.08,112.50) --
	(236.65,116.23) --
	(242.22,130.94) --
	(247.78,168.51);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (197.68, 68.42) --
	(203.25, 63.98) --
	(208.82, 63.98) --
	(214.38, 63.98);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (195.72,111.28) --
	(199.65,111.28) --
	(199.65,115.20) --
	(195.72,115.20) --
	cycle;

\path[fill=fillColor] (201.29,109.89) --
	(205.21,109.89) --
	(205.21,113.82) --
	(201.29,113.82) --
	cycle;

\path[fill=fillColor] (206.86,109.63) --
	(210.78,109.63) --
	(210.78,113.55) --
	(206.86,113.55) --
	cycle;

\path[fill=fillColor] (212.42,109.70) --
	(216.35,109.70) --
	(216.35,113.62) --
	(212.42,113.62) --
	cycle;

\path[fill=fillColor] (217.99,110.16) --
	(221.91,110.16) --
	(221.91,114.09) --
	(217.99,114.09) --
	cycle;

\path[fill=fillColor] (223.56,110.31) --
	(227.48,110.31) --
	(227.48,114.23) --
	(223.56,114.23) --
	cycle;

\path[fill=fillColor] (229.12,110.53) --
	(233.05,110.53) --
	(233.05,114.46) --
	(229.12,114.46) --
	cycle;

\path[fill=fillColor] (234.69,114.27) --
	(238.61,114.27) --
	(238.61,118.20) --
	(234.69,118.20) --
	cycle;

\path[fill=fillColor] (240.26,128.97) --
	(244.18,128.97) --
	(244.18,132.90) --
	(240.26,132.90) --
	cycle;

\path[fill=fillColor] (245.82,166.55) --
	(249.75,166.55) --
	(249.75,170.47) --
	(245.82,170.47) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (197.68, 90.42) --
	(200.33, 85.84) --
	(195.04, 85.84) --
	cycle;

\path[fill=fillColor] (203.25, 90.41) --
	(205.89, 85.84) --
	(200.61, 85.84) --
	cycle;

\path[fill=fillColor] (208.82, 90.41) --
	(211.46, 85.84) --
	(206.18, 85.84) --
	cycle;

\path[fill=fillColor] (214.38, 90.41) --
	(217.03, 85.84) --
	(211.74, 85.84) --
	cycle;

\path[fill=fillColor] (219.95, 90.41) --
	(222.59, 85.84) --
	(217.31, 85.84) --
	cycle;

\path[fill=fillColor] (225.52, 90.41) --
	(228.16, 85.84) --
	(222.88, 85.84) --
	cycle;

\path[fill=fillColor] (231.08, 90.42) --
	(233.73, 85.84) --
	(228.44, 85.84) --
	cycle;

\path[fill=fillColor] (236.65, 90.49) --
	(239.29, 85.92) --
	(234.01, 85.92) --
	cycle;

\path[fill=fillColor] (242.22, 91.39) --
	(244.86, 86.82) --
	(239.57, 86.82) --
	cycle;

\path[fill=fillColor] (247.78,100.21) --
	(250.43, 95.64) --
	(245.14, 95.64) --
	cycle;

\path[fill=fillColor] (253.35,126.40) --
	(255.99,121.82) --
	(250.71,121.82) --
	cycle;

\path[fill=fillColor] (258.92,160.59) --
	(261.56,156.02) --
	(256.27,156.02) --
	cycle;

\path[fill=fillColor] (264.48,195.39) --
	(267.13,190.81) --
	(261.84,190.81) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91, 68.42) -- (200.46, 68.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.68, 65.64) -- (197.68, 71.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.48, 63.98) -- (206.03, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.25, 61.20) -- (203.25, 66.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.04, 63.98) -- (211.59, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.82, 61.20) -- (208.82, 66.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.61, 63.98) -- (217.16, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.38, 61.20) -- (214.38, 66.75);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (197.68, 87.62) circle (  1.96);

\path[fill=fillColor] (203.25, 87.61) circle (  1.96);

\path[fill=fillColor] (208.82, 87.61) circle (  1.96);

\path[fill=fillColor] (214.38, 87.61) circle (  1.96);

\path[fill=fillColor] (219.95, 87.61) circle (  1.96);

\path[fill=fillColor] (225.52, 87.61) circle (  1.96);

\path[fill=fillColor] (231.08, 87.62) circle (  1.96);

\path[fill=fillColor] (236.65, 87.69) circle (  1.96);

\path[fill=fillColor] (242.22, 88.58) circle (  1.96);

\path[fill=fillColor] (247.78, 97.29) circle (  1.96);

\path[fill=fillColor] (253.35,123.32) circle (  1.96);

\path[fill=fillColor] (258.92,157.55) circle (  1.96);

\path[fill=fillColor] (264.48,192.33) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.27, 89.52) --
	(360.83, 89.52) --
	(366.40, 89.52) --
	(371.97, 89.52) --
	(377.53, 89.52) --
	(383.10, 89.52) --
	(388.67, 89.52) --
	(394.23, 89.52) --
	(399.80, 89.52) --
	(405.37, 89.52) --
	(410.93, 89.52) --
	(416.50, 89.52) --
	(422.07, 89.53) --
	(427.63, 89.55) --
	(433.20, 89.61) --
	(438.77, 89.71) --
	(444.33, 89.97) --
	(449.90, 90.65) --
	(455.47, 92.11) --
	(461.03, 95.47) --
	(466.60,101.07) --
	(472.17,108.80) --
	(477.73,119.46) --
	(483.30,132.70) --
	(488.87,144.57) --
	(494.43,157.31);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (355.27, 88.43) --
	(360.83, 88.43) --
	(366.40, 88.43) --
	(371.97, 88.43) --
	(377.53, 88.43) --
	(383.10, 88.43) --
	(388.67, 88.43) --
	(394.23, 88.43) --
	(399.80, 88.43) --
	(405.37, 88.43) --
	(410.93, 88.43) --
	(416.50, 88.43) --
	(422.07, 88.44) --
	(427.63, 88.46) --
	(433.20, 88.51) --
	(438.77, 88.64) --
	(444.33, 88.92) --
	(449.90, 89.63) --
	(455.47, 91.16) --
	(461.03, 94.48) --
	(466.60,100.45) --
	(472.17,108.29) --
	(477.73,119.14) --
	(483.30,132.38) --
	(488.87,144.46) --
	(494.43,157.43);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (355.27,114.65) --
	(360.83,111.15) --
	(366.40,111.49) --
	(371.97,111.10) --
	(377.53,115.68) --
	(383.10,162.17);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (355.27, 66.36) --
	(360.83, 64.61) --
	(366.40, 64.61) --
	(371.97, 64.61) --
	(377.53, 64.61) --
	(383.10, 64.92) --
	(388.67, 64.92);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (355.27, 89.52) circle (  1.96);

\path[fill=fillColor] (360.83, 89.52) circle (  1.96);

\path[fill=fillColor] (366.40, 89.52) circle (  1.96);

\path[fill=fillColor] (371.97, 89.52) circle (  1.96);

\path[fill=fillColor] (377.53, 89.52) circle (  1.96);

\path[fill=fillColor] (383.10, 89.52) circle (  1.96);

\path[fill=fillColor] (388.67, 89.52) circle (  1.96);

\path[fill=fillColor] (394.23, 89.52) circle (  1.96);

\path[fill=fillColor] (399.80, 89.52) circle (  1.96);

\path[fill=fillColor] (405.37, 89.52) circle (  1.96);

\path[fill=fillColor] (410.93, 89.52) circle (  1.96);

\path[fill=fillColor] (416.50, 89.52) circle (  1.96);

\path[fill=fillColor] (422.07, 89.53) circle (  1.96);

\path[fill=fillColor] (427.63, 89.55) circle (  1.96);

\path[fill=fillColor] (433.20, 89.61) circle (  1.96);

\path[fill=fillColor] (438.77, 89.71) circle (  1.96);

\path[fill=fillColor] (444.33, 89.97) circle (  1.96);

\path[fill=fillColor] (449.90, 90.65) circle (  1.96);

\path[fill=fillColor] (455.47, 92.11) circle (  1.96);

\path[fill=fillColor] (461.03, 95.47) circle (  1.96);

\path[fill=fillColor] (466.60,101.07) circle (  1.96);

\path[fill=fillColor] (472.17,108.80) circle (  1.96);

\path[fill=fillColor] (477.73,119.46) circle (  1.96);

\path[fill=fillColor] (483.30,132.70) circle (  1.96);

\path[fill=fillColor] (488.87,144.57) circle (  1.96);

\path[fill=fillColor] (494.43,157.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.49, 66.36) -- (358.04, 66.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.27, 63.59) -- (355.27, 69.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (358.06, 64.61) -- (363.61, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.83, 61.83) -- (360.83, 67.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (363.62, 64.61) -- (369.17, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.40, 61.83) -- (366.40, 67.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.19, 64.61) -- (374.74, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.97, 61.83) -- (371.97, 67.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.76, 64.61) -- (380.31, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.53, 61.83) -- (377.53, 67.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (380.32, 64.92) -- (385.87, 64.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.10, 62.14) -- (383.10, 67.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.89, 64.92) -- (391.44, 64.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.67, 62.14) -- (388.67, 67.69);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (353.30,112.68) --
	(357.23,112.68) --
	(357.23,116.61) --
	(353.30,116.61) --
	cycle;

\path[fill=fillColor] (358.87,109.19) --
	(362.80,109.19) --
	(362.80,113.11) --
	(358.87,113.11) --
	cycle;

\path[fill=fillColor] (364.44,109.53) --
	(368.36,109.53) --
	(368.36,113.45) --
	(364.44,113.45) --
	cycle;

>>>>

% Created by tikzDevice version 0.12.6 on 2024-08-15 12:12:55
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,123.48) --
	( 45.67,112.22) --
	( 51.24,112.22) --
	( 56.80,112.42) --
	( 62.37,119.02) --
	( 67.94,162.96);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.10,106.36) --
	( 45.67,106.36) --
	( 51.24,106.36) --
	( 56.80,106.36) --
	( 62.37,106.36) --
	( 67.94,106.37) --
	( 73.50,106.38) --
	( 79.07,106.42) --
	( 84.64,106.58) --
	( 90.20,107.23) --
	( 95.77,109.99) --
	(101.34,117.90);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 38.14,104.40) --
	( 42.06,104.40) --
	( 42.06,108.33) --
	( 38.14,108.33) --
	cycle;

\path[fill=fillColor] ( 43.71,104.40) --
	( 47.63,104.40) --
	( 47.63,108.33) --
	( 43.71,108.33) --
	cycle;

\path[fill=fillColor] ( 49.27,104.40) --
	( 53.20,104.40) --
	( 53.20,108.33) --
	( 49.27,108.33) --
	cycle;

\path[fill=fillColor] ( 54.84,104.40) --
	( 58.76,104.40) --
	( 58.76,108.33) --
	( 54.84,108.33) --
	cycle;

\path[fill=fillColor] ( 60.41,104.40) --
	( 64.33,104.40) --
	( 64.33,108.33) --
	( 60.41,108.33) --
	cycle;

\path[fill=fillColor] ( 65.97,104.40) --
	( 69.90,104.40) --
	( 69.90,108.33) --
	( 65.97,108.33) --
	cycle;

\path[fill=fillColor] ( 71.54,104.41) --
	( 75.46,104.41) --
	( 75.46,108.34) --
	( 71.54,108.34) --
	cycle;

\path[fill=fillColor] ( 77.11,104.45) --
	( 81.03,104.45) --
	( 81.03,108.38) --
	( 77.11,108.38) --
	cycle;

\path[fill=fillColor] ( 82.67,104.62) --
	( 86.60,104.62) --
	( 86.60,108.54) --
	( 82.67,108.54) --
	cycle;

\path[fill=fillColor] ( 88.24,105.27) --
	( 92.16,105.27) --
	( 92.16,109.19) --
	( 88.24,109.19) --
	cycle;

\path[fill=fillColor] ( 93.81,108.02) --
	( 97.73,108.02) --
	( 97.73,111.95) --
	( 93.81,111.95) --
	cycle;

\path[fill=fillColor] ( 99.37,115.94) --
	(103.30,115.94) --
	(103.30,119.87) --
	( 99.37,119.87) --
	cycle;
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 40.10,123.48) circle (  1.96);

\path[fill=fillColor] ( 45.67,112.22) circle (  1.96);

\path[fill=fillColor] ( 51.24,112.22) circle (  1.96);

\path[fill=fillColor] ( 56.80,112.42) circle (  1.96);

\path[fill=fillColor] ( 62.37,119.02) circle (  1.96);

\path[fill=fillColor] ( 67.94,162.96) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.68,113.24) --
	(203.25,111.85) --
	(208.82,111.59) --
	(214.38,111.66) --
	(219.95,112.12) --
	(225.52,112.27) --
	(231.08,112.50) --
	(236.65,116.23) --
	(242.22,130.94) --
	(247.78,168.51);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 68.42) --
	(203.25, 63.98) --
	(208.82, 63.98) --
	(214.38, 63.98);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (197.68, 87.62) --
	(203.25, 87.61) --
	(208.82, 87.61) --
	(214.38, 87.61) --
	(219.95, 87.61) --
	(225.52, 87.61) --
	(231.08, 87.62) --
	(236.65, 87.69) --
	(242.22, 88.58) --
	(247.78, 97.29) --
	(253.35,123.32) --
	(258.92,157.55) --
	(264.48,192.33);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (197.68, 87.37) --
	(203.25, 87.36) --
	(208.82, 87.36) --
	(214.38, 87.36) --
	(219.95, 87.36) --
	(225.52, 87.36) --
	(231.08, 87.37) --
	(236.65, 87.44) --
	(242.22, 88.34) --
	(247.78, 97.16) --
	(253.35,123.35) --
	(258.92,157.54) --
	(264.48,192.33);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (197.68,113.24) circle (  1.96);

\path[fill=fillColor] (203.25,111.85) circle (  1.96);

\path[fill=fillColor] (208.82,111.59) circle (  1.96);

\path[fill=fillColor] (214.38,111.66) circle (  1.96);

\path[fill=fillColor] (219.95,112.12) circle (  1.96);

\path[fill=fillColor] (225.52,112.27) circle (  1.96);

\path[fill=fillColor] (231.08,112.50) circle (  1.96);

\path[fill=fillColor] (236.65,116.23) circle (  1.96);

\path[fill=fillColor] (242.22,130.94) circle (  1.96);

\path[fill=fillColor] (247.78,168.51) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91, 87.37) -- (200.46, 87.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.68, 84.59) -- (197.68, 90.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.48, 87.36) -- (206.03, 87.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.25, 84.59) -- (203.25, 90.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.04, 87.36) -- (211.59, 87.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.82, 84.59) -- (208.82, 90.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.61, 87.36) -- (217.16, 87.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.38, 84.59) -- (214.38, 90.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.18, 87.36) -- (222.73, 87.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.95, 84.59) -- (219.95, 90.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.74, 87.36) -- (228.29, 87.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.52, 84.59) -- (225.52, 90.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.31, 87.37) -- (233.86, 87.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.08, 84.59) -- (231.08, 90.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.88, 87.44) -- (239.43, 87.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.65, 84.67) -- (236.65, 90.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.44, 88.34) -- (244.99, 88.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.22, 85.57) -- (242.22, 91.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.01, 97.16) -- (250.56, 97.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.78, 94.39) -- (247.78, 99.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.58,123.35) -- (256.13,123.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.35,120.57) -- (253.35,126.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.14,157.54) -- (261.69,157.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.92,154.77) -- (258.92,160.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.71,192.33) -- (267.26,192.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.48,189.56) -- (264.48,195.11);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (197.68, 71.47) --
	(200.33, 66.89) --
	(195.04, 66.89) --
	cycle;

\path[fill=fillColor] (203.25, 67.03) --
	(205.89, 62.45) --
	(200.61, 62.45) --
	cycle;

\path[fill=fillColor] (208.82, 67.03) --
	(211.46, 62.45) --
	(206.18, 62.45) --
	cycle;

\path[fill=fillColor] (214.38, 67.03) --
	(217.03, 62.45) --
	(211.74, 62.45) --
	cycle;
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (195.72, 85.66) --
	(199.65, 85.66) --
	(199.65, 89.58) --
	(195.72, 89.58) --
	cycle;

\path[fill=fillColor] (201.29, 85.65) --
	(205.21, 85.65) --
	(205.21, 89.58) --
	(201.29, 89.58) --
	cycle;

\path[fill=fillColor] (206.86, 85.65) --
	(210.78, 85.65) --
	(210.78, 89.58) --
	(206.86, 89.58) --
	cycle;

\path[fill=fillColor] (212.42, 85.65) --
	(216.35, 85.65) --
	(216.35, 89.58) --
	(212.42, 89.58) --
	cycle;

\path[fill=fillColor] (217.99, 85.65) --
	(221.91, 85.65) --
	(221.91, 89.58) --
	(217.99, 89.58) --
	cycle;

\path[fill=fillColor] (223.56, 85.65) --
	(227.48, 85.65) --
	(227.48, 89.58) --
	(223.56, 89.58) --
	cycle;

\path[fill=fillColor] (229.12, 85.66) --
	(233.05, 85.66) --
	(233.05, 89.58) --
	(229.12, 89.58) --
	cycle;

\path[fill=fillColor] (234.69, 85.73) --
	(238.61, 85.73) --
	(238.61, 89.66) --
	(234.69, 89.66) --
	cycle;

\path[fill=fillColor] (240.26, 86.62) --
	(244.18, 86.62) --
	(244.18, 90.54) --
	(240.26, 90.54) --
	cycle;

\path[fill=fillColor] (245.82, 95.32) --
	(249.75, 95.32) --
	(249.75, 99.25) --
	(245.82, 99.25) --
	cycle;

\path[fill=fillColor] (251.39,121.35) --
	(255.31,121.35) --
	(255.31,125.28) --
	(251.39,125.28) --
	cycle;

\path[fill=fillColor] (256.96,155.59) --
	(260.88,155.59) --
	(260.88,159.51) --
	(256.96,159.51) --
	cycle;

\path[fill=fillColor] (262.52,190.37) --
	(266.45,190.37) --
	(266.45,194.30) --
	(262.52,194.30) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.27,114.65) --
	(360.83,111.15) --
	(366.40,111.49) --
	(371.97,111.10) --
	(377.53,115.68) --
	(383.10,162.17);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (355.27, 66.36) --
	(360.83, 64.61) --
	(366.40, 64.61) --
	(371.97, 64.61) --
	(377.53, 64.61) --
	(383.10, 64.92) --
	(388.67, 64.92);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (355.27, 89.52) --
	(360.83, 89.52) --
	(366.40, 89.52) --
	(371.97, 89.52) --
	(377.53, 89.52) --
	(383.10, 89.52) --
	(388.67, 89.52) --
	(394.23, 89.52) --
	(399.80, 89.52) --
	(405.37, 89.52) --
	(410.93, 89.52) --
	(416.50, 89.52) --
	(422.07, 89.53) --
	(427.63, 89.55) --
	(433.20, 89.61) --
	(438.77, 89.71) --
	(444.33, 89.97) --
	(449.90, 90.65) --
	(455.47, 92.11) --
	(461.03, 95.47) --
	(466.60,101.07) --
	(472.17,108.80) --
	(477.73,119.46) --
	(483.30,132.70) --
	(488.87,144.57) --
	(494.43,157.31);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (355.27, 88.43) --
	(360.83, 88.43) --
	(366.40, 88.43) --
	(371.97, 88.43) --
	(377.53, 88.43) --
	(383.10, 88.43) --
	(388.67, 88.43) --
	(394.23, 88.43) --
	(399.80, 88.43) --
	(405.37, 88.43) --
	(410.93, 88.43) --
	(416.50, 88.43) --
	(422.07, 88.44) --
	(427.63, 88.46) --
	(433.20, 88.51) --
	(438.77, 88.64) --
	(444.33, 88.92) --
	(449.90, 89.63) --
	(455.47, 91.16) --
	(461.03, 94.48) --
	(466.60,100.45) --
	(472.17,108.29) --
	(477.73,119.14) --
	(483.30,132.38) --
	(488.87,144.46) --
	(494.43,157.43);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (353.30, 87.55) --
	(357.23, 87.55) --
	(357.23, 91.48) --
	(353.30, 91.48) --
	cycle;

\path[fill=fillColor] (358.87, 87.55) --
	(362.80, 87.55) --
	(362.80, 91.48) --
	(358.87, 91.48) --
	cycle;

\path[fill=fillColor] (364.44, 87.55) --
	(368.36, 87.55) --
	(368.36, 91.48) --
	(364.44, 91.48) --
	cycle;

\path[fill=fillColor] (370.00, 87.55) --
	(373.93, 87.55) --
	(373.93, 91.48) --
	(370.00, 91.48) --
	cycle;

\path[fill=fillColor] (375.57, 87.55) --
	(379.50, 87.55) --
	(379.50, 91.48) --
	(375.57, 91.48) --
	cycle;

\path[fill=fillColor] (381.14, 87.56) --
	(385.06, 87.56) --
	(385.06, 91.48) --
	(381.14, 91.48) --
	cycle;

\path[fill=fillColor] (386.70, 87.55) --
	(390.63, 87.55) --
	(390.63, 91.48) --
	(386.70, 91.48) --
	cycle;

\path[fill=fillColor] (392.27, 87.55) --
	(396.19, 87.55) --
	(396.19, 91.48) --
	(392.27, 91.48) --
	cycle;

\path[fill=fillColor] (397.84, 87.55) --
	(401.76, 87.55) --
	(401.76, 91.48) --
	(397.84, 91.48) --
	cycle;

\path[fill=fillColor] (403.40, 87.56) --
	(407.33, 87.56) --
	(407.33, 91.48) --
	(403.40, 91.48) --
	cycle;

\path[fill=fillColor] (408.97, 87.56) --
	(412.89, 87.56) --
	(412.89, 91.48) --
	(408.97, 91.48) --
	cycle;

\path[fill=fillColor] (414.54, 87.56) --
	(418.46, 87.56) --
	(418.46, 91.48) --
	(414.54, 91.48) --
	cycle;

\path[fill=fillColor] (420.10, 87.57) --
	(424.03, 87.57) --
	(424.03, 91.50) --
	(420.10, 91.50) --
	cycle;

\path[fill=fillColor] (425.67, 87.58) --
	(429.59, 87.58) --
	(429.59, 91.51) --
	(425.67, 91.51) --
	cycle;

\path[fill=fillColor] (431.24, 87.64) --
	(435.16, 87.64) --
	(435.16, 91.57) --
	(431.24, 91.57) --
	cycle;

\path[fill=fillColor] (436.80, 87.75) --
	(440.73, 87.75) --
	(440.73, 91.67) --
	(436.80, 91.67) --
	cycle;

\path[fill=fillColor] (442.37, 88.01) --
	(446.29, 88.01) --
	(446.29, 91.94) --
	(442.37, 91.94) --
	cycle;

\path[fill=fillColor] (447.94, 88.69) --
	(451.86, 88.69) --
	(451.86, 92.61) --
	(447.94, 92.61) --
	cycle;

\path[fill=fillColor] (453.50, 90.15) --
	(457.43, 90.15) --
	(457.43, 94.07) --
	(453.50, 94.07) --
	cycle;

\path[fill=fillColor] (459.07, 93.51) --
	(462.99, 93.51) --
	(462.99, 97.43) --
	(459.07, 97.43) --
	cycle;

\path[fill=fillColor] (464.64, 99.11) --
	(468.56, 99.11) --
	(468.56,103.03) --
	(464.64,103.03) --
	cycle;

\path[fill=fillColor] (470.20,106.84) --
	(474.13,106.84) --
	(474.13,110.76) --
	(470.20,110.76) --
	cycle;

\path[fill=fillColor] (475.77,117.50) --
	(479.69,117.50) --
	(479.69,121.43) --
	(475.77,121.43) --
	cycle;

\path[fill=fillColor] (481.34,130.74) --
	(485.26,130.74) --
	(485.26,134.66) --
	(481.34,134.66) --
	cycle;

\path[fill=fillColor] (486.90,142.61) --
	(490.83,142.61) --
	(490.83,146.54) --
	(486.90,146.54) --
	cycle;

\path[fill=fillColor] (492.47,155.35) --
	(496.39,155.35) --
	(496.39,159.27) --
	(492.47,159.27) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}
